Verification of Stencil Computations with Spatial Specifications

### 2016-11-14 paper.tex
Reduce verbosity of main features of the tool

We provide a verification tool for such specifications which can check
the correctness of code against the specification, and can also infer
specifications, synthesising these as comments in the
source code. The main features and benefits of our approach are as follows:
%
\begin{itemize}
\item The main use case is that a programmers writes a specification
  first (perhaps informed by their numerical analysis), then writes
  the corresponding source code, and lastly has the tool check its
  conformance to the specifications. This specify-and-check approach
  removes the usually ad hoc testing effort, and provides the
  opportunity for easy re-verification in the event of any refactoring
  of software maintenance activities.
%
\item The specification provides a concise description which can be
  preserved in the source code to provide documentation to future
  developers, contrasting with ad hoc tests which are usually
  discarded or specialised to the development environment. Separate from the
  verification procedure, the infer-and-synthesise mode of the tool
  provides a way to automatically generate additional useful
  documentation for future users.
%
\item Specifications are integrated into the code as comments for easy
integration with existing tools, as well as
  documentation systems (\eg{}, we support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small
  number of combinators that \emph{do not involve any indexing
    expressions}, \eg{} does not involve expressions like
  \texttt{a(i+1,j-1)}. This contrasts with other specification
  approaches.% For example, the work of Kamil et al.~\cite{kamil2016verified}
  %provides full-functionality specifications of stencil computations
  %in the form of a domain-specific language.  
  If a user wishes to specify, say, the
  Naiver-Stokes stencil above, in a deductive verification languages
  like ACSL, they must write a specification which is very
  similar to the code, involving textually dense array-indexing expressions. Therefore any
  low-level mistakes that could be made whilst programming complex indexing code could
  also be made when writing a specification. Our specifications are much more
  abstract, and also more lightweight with the aim of aiding adoption by
  scientists.
\end{itemize}

>>>>

We provide a verification tool which can check the correctness of stencil code
against its specification, infer such specifications from bare source, and
synthese inferred specifications as comments and insert them into the source
code. The main features and benefits of our approach are as follows:
%
\begin{itemize}
%\item The main use case is that a programmer writes a specification
%  first (perhaps informed by their numerical analysis), then writes
%  the corresponding source code, and lastly has the tool check its
%  conformance to the specifications. This specify-and-check approach
%  removes the usually ad hoc testing effort, and provides the
%  opportunity for easy re-verification in the event of any refactoring
%  of software maintenance activities.
\item The primary use case is that a programmer writes a specification first,
  then the corresponding source code and the tool checks conformance between
  the two. This specify-and-check approach reduces the testing effort and
  future-proofs against bugs introduced during refactoring and maintanence.
%
%\item The specification provides a concise description which can be
%  preserved in the source code to provide documentation to future
%  developers, contrasting with ad hoc tests which are usually
%  discarded or specialised to the development environment. Separate from the
%  verification procedure, the infer-and-synthesise mode of the tool
%  provides a way to automatically generate additional useful
%  documentation for future users.

% Emphasis here is on documentation generation, so it makes little sense to
% compare this aspect of CamFort to ad hoc testing. Apples and oranges.
\item A specification concisely captures the access pattern and turns it into
  documentation. Inference algorithm efficiently produces specifications with
  no programmer intervention, while synthesis mechanism inserts the
  specifications at appropriate places in the source code automatically.
%
\item Specifications are integrated into the code as comments for easy
  integration with existing tools, as well as documentation systems (\eg{}, we
  support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small number of
  combinators that \emph{do not involve any indexing expressions}, \eg{}
  \texttt{a(i+1,j-1)}. This contrasts with other specification approaches. If a
  user specifies, say, the Naiver-Stokes stencil above, in a deductive
  verification language such as ACSL, they must write a specification involving
  textually dense array-indexing expressions. Therefore, any low-level mistakes
  that could be made whilst programming complex indexing code could also be
  made when writing its specification. Our specifications are more abstract and
  lightweight with the aim of aiding adoption by scientists and preventing
  indexing errors.
\end{itemize}
